%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Freeman Curriculum Vitae
% XeLaTeX Template
% Version 2.0 (19/3/2018)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Vel (vel@LaTeXTemplates.com)
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%!TEX program = xelatex
% NOTICE: This template must be compiled with XeLaTeX, the line above should
% ensure this happens automatically but if it doesn't you will need to specify
% XeLaTeX as the engine in your editor or script
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Font size, can be: 10pt, 11pt or 12pt

\input{structure.tex} % Include the file that specifies the document structure

% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example right footer:
%\rfoot{\color{headings}{\sffamily Last update: \today. Typeset with Xe\LaTeX}}

%----------------------------------------------------------------------------------------

\begin{document}

\begin{paracol}{2} % Begin the multi-column environment

%----------------------------------------------------------------------------------------
%	NAME AND CURRICULUM VITAE TEXT
%----------------------------------------------------------------------------------------

\parbox[top][0.12\textheight][c]{\linewidth}{ % Parbox to hold the author name and CV text; fixed height to match the coloured box to the right, centred vertically and full line width
	\vspace{-0.04\textheight} % Reduce whitespace above the parbox to separate it from the main content
	\centering % Centre text
	{\sffamily\Huge Giuseppe Baccini}\\\medskip % Your name
	{\Huge\color{headings}\cvtextfont Curriculum Vitae}
}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Work Experience}

% Blank \workposition command to add another job:

%\workposition{} % Duration
%{} % FT/PT (full time or part time)
%{} % Employer
%{} % Job title
%{} % Description

% All 5 parameters must be supplied but any can be empty if you don't need them

%------------------------------------------------

\workposition{Feb 2024 -- Current} % Duration
{FT} % FT/PT (full time or part time)
{LogObject AG} % Employer
{Senior Software Architect, Senior Staff Engineer} % Job title
{As a member of the Design and Development team for the mLogistics product — a proprietary platform
tailored to implement logistics solutions for large-scale organizations — I am responsible for
architecting the next-generation system to meet evolving modern requirements.
The platform primarily leverages a Java-based technology stack alongside Oracle and PostgreSQL
database management systems.
In my role as Staff Engineer, I have designed a solution using Docker Compose to streamline environment
management for developers. This solution enables them to create, consume, and produce environments
efficiently while making these environments accessible to the entire team.
Additionally, I have designed a robust solution for emergency video calls utilized by emergency services,
employing an architecture that integrates Coturn for TURN server functionality, Envoy for service proxying,
and Redis for session management.}

\workposition{Feb 2022 -- Dec 2023} % Duration
{FT} % FT/PT (full time or part time)
{SUSE (Software Defined Storage)} % Employer
{Senior Software Engineer} % Job title
{At SUSE, I was part of the development team for the Enterprise Storage solution, contributing
to the SUSE Enterprise Storage (SES) distribution and the Ceph platform. Ceph is a free and open-source
software-defined storage platform that provides object, block, and file storage on a unified,
distributed cluster foundation. It is designed for fully distributed operations without a single point of
failure and offers scalability to the exabyte level.
Additionally, I contributed to the software development of the s3gw and Epinio projects.
The s3gw is an S3-compatible service optimized for Kubernetes environments, leveraging Persistent Volume
Claims (PVCs) such as Longhorn.
Epinio is a developer platform simplifying the deployment of applications in Kubernetes.
These experiences allowed me to develop expertise in a range of technologies and tools, including
Golang, SQLite, S3, Docker, Podman, Git, GitHub, Kubernetes, K3s, K3d, Longhorn, Rancher,
Custom Resource Definitions (CRDs), Helm, Vagrant, Ansible, and libvirt.} % Description

\switchcolumn % Switch to the next paracol column

\parbox[top][0.12\textheight][c]{\linewidth}{ % Parbox to hold the colour box; fixed height to match the name/CV text to the left, centred vertically and full line width
	\vspace{-0.04\textheight} % Reduce whitespace above the parbox to separate it from the main content
	\colorbox{shade}{ % Create the coloured box
		\begin{supertabular}{p{0.05\linewidth}|p{0.775\linewidth}} % Start a table with two columns, the table will ensure everything is aligned
			\raisebox{-1pt}{\faHome} & Via Toniolo 5, Carrara, 54033, Italy \\ % Address
			\raisebox{-1pt}{\faPhone} & +39 3288143657 \\ % Phone number
			\raisebox{0pt}{\small\faEnvelope} & \href{mailto:giuseppe.baccini@live.com}{giuseppe.baccini@live.com} \\ % Email address
			\raisebox{-1pt}{\faGithub} & \href{https://github.com/giubacc}{giubacc} \\ % GitHub profile
			\raisebox{-1pt}{\faLinkedinSquare} & \href{https://www.linkedin.com/in/giuseppe-baccini-0288687}{Giuseppe Baccini} \\ % LinkedIn profile
			% See fontawesome.pdf in the fonts folder for all icons you can use
		\end{supertabular}
	}
}
\\
\\
\\
\\
\workpositionmain{2010 -- 2022} % Duration
{FT}
{LIST S.p.A} % Employer
{Capital Market Products}
{Engineering}
{During my tenure in the Products division of LIST (Italy, Spain), I have taken on various roles and
responsibilities, contributing significantly to numerous product development initiatives.
I played an active role in implementing solutions based on the FastTrade product suite—a modular,
multi-asset platform designed for the development of electronic trading systems.
Over the course of this decade-long experience, I acquired extensive expertise in a wide range of
industry-standard technologies, including C/C++, Boost, Java, Spring Boot, Python, RDBMS, Cassandra,
Message Broker systems, AMQP, MQTT, Git, Kubernetes, Docker, CI/CD pipelines, and many others.
This period has honed my technical skills and deepened my understanding of the tools and methodologies
essential for building scalable, high-performance trading systems.}
%------------------------------------------------

\workposition{2019 -- 2022} % Duration
{FT} % FT/PT (full time or part time)
{LIST S.p.A (Capital Market Products)} % Employer
{Senior Software Engineer} % Job title
{As a member of the Design and Development Team responsible for the connectivity layer of the FastTrade
product, I played a key role in designing, developing, and enhancing various software gateways—fundamental
building blocks of the FastTrade trading platform—tailored for integration with major European trading venues.
In addition to my work on gateways, I contributed to the development of several core structural components,
further strengthening the platform's scalability, reliability, and adaptability to the demanding requirements
of electronic trading environments.
} %  Description

%------------------------------------------------
\workposition{2018 -- 2019} % Duration
{FT} % FT/PT (full time or part time)
{LIST S.p.A (Capital Market Products)} % Employer
{Senior Software Engineer} % Job title
{As a member of the Design and Development Team for the FTX-FastTrade Exchange product — a software solution
designed to facilitate the implementation of Trading Venues and Systematic Internalisers in alignment
with MiFID II regulations — I played an active role in expanding the suite's support for diverse market models.
My specific contributions included the design and development of an RFQ (Request for Quote) model with
third-party account management, enabling greater flexibility and functionality within the FTX suite to
meet the evolving needs of trading venues.} % Description

\switchcolumn
\newpage

\section{Work Experience}

%------------------------------------------------
\workposition{2016 -- 2018} % Duration
{FT} % FT/PT (full time or part time)
{LIST S.p.A (Capital Market Products)} % Employer
{Senior Software Engineer} % Job title
{As a Software Architect in the Design and Development Team for the FastTrade MetaMarket product, I was responsible
for the end-to-end design, development, testing, and optimization of key technological, architectural,
and functional components within the FastTrade product suite.
My role encompassed not only crafting high-performance, resilient solutions but also fine-tuning the platform
for scalability and robustness to meet the demanding requirements of modern electronic trading systems.} % Description

%------------------------------------------------
\workposition{2014 -- 2016} % Duration
{FT} % FT/PT (full time or part time)
{LIST Spain. (LIST Branch)} % Employer
{Senior Software Engineer, Transfer Manager} % Job title
{As a member of the Design and Development Team and Technology Transfer Manager representing the parent company,
LIST S.p.A., I contributed to the development of the FastTrade Deal Manager product.
This effort was part of a major project to deliver a comprehensive solution for managing trading flows of financial
contracts executed across all global branches and locations of BBVA (Banco Bilbao Vizcaya Argentaria, S.A.).
My role involved ensuring seamless integration, knowledge transfer, and the successful deployment of this critical
trading infrastructure within BBVA's extensive international network.} % Description

%------------------------------------------------
\workposition{2013 -- 2014} % Duration
{FT} % FT/PT (full time or part time)
{LIST S.p.A. (Capital Market Products)} % Employer
{Contingency Team Manager} % Job title
{I served as the Contingency Team Leader within the Product Division, where I was responsible for managing
high-priority interventions in the software library. This role encompassed direct customer management,
issue resolution, and the coordination of development teams within the Product Department to address critical
issues efficiently and effectively.} % Description

%------------------------------------------------
\workposition{2011 -- 2013} % Duration
{FT} % FT/PT (full time or part time)
{LIST S.p.A. (Capital Market Products)} % Employer
{Software Engineer} % Job title
{As a member of the Design and Development Team for the FastTrade Payment solution—covering the Greek Payment
System, Credit Transfer, and Direct Debit—I contributed to a project focused on integrating, interconnecting,
and modernizing national payment systems to align with SEPA (Single Euro Payments Area) standards.
My work involved ensuring seamless compliance and harmonization across diverse financial systems, supporting
the transition to a unified European payment framework.} % Description

\switchcolumn
\newpage

\par
\vspace*{0.5cm}

%------------------------------------------------
\workposition{2010 -- 2011} % Duration
{FT} % FT/PT (full time or part time)
{LIST S.p.A. (Capital Market Products)} % Employer
{Software Engineer} % Job title
{As a member of the Design and Development Team for the FastTrade OMS (Order Manager System) product — focused
on the electronic trading of financial instruments—I played a key role in the implementation and deployment of the
SaaS service MarketHUB, developed for Intesa Sanpaolo.
My contributions ensured the successful delivery of this advanced trading platform, tailored to meet the bank's
requirements and provide seamless electronic trading capabilities.} % Description

\workposition{2008 -- 2010} % Duration
{FT} % FT/PT (full time or part time)
{RJC Soft S.r.l} % Employer
{Software Engineer} % Job title
{As a member of the team responsible for developing and maintaining Telecom Italia's user profiling system,
I actively contributed to implementing a solution leveraging the Oracle Coherence distributed caching system.
This approach enhanced the system's scalability, performance, and reliability, ensuring efficient handling
of user data across a distributed infrastructure.} % Description

\workposition{2007 -- 2008} % Duration
{FT} % FT/PT (full time or part time)
{Apai S.r.l} % Employer
{Software Engineer} % Job title
{In my first professional role, I served as a member of the Design and Development Team responsible for
developing and maintaining Intesa Sanpaolo's employee access and authorization system.
This experience marked the beginning of my career, providing me with valuable hands-on exposure to designing
secure and efficient systems for managing access control within a large-scale organization.} % Description

%------------------------------------------------

\vspace{-\baselineskip}\medskip % Standardise the whitespace after this section and before the next (the custom command adds too much otherwise)

\switchcolumn % Switch to the next paracol column
\newpage

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	COLOURED CONTACT DETAILS BOX
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

% Blank \educationentry{} command to add another degree:

%\educationentry{} % Duration
%{} % Degree
%{} % Honours, achievements or distinctions (e.g. first class honours)
%{} % Department
%{} % Institution

% All 5 parameters must be supplied but any can be empty if you don't need them

%------------------------------------------------

\begin{supertabular}{rl} % Start a table with two columns, the table will ensure everything is aligned

	%------------------------------------------------

	\educationentry{2006} % Duration
	{Bachelor of Computer Science} % Degree
	{} % Honours, achievements or distinctions (e.g. first class honours)
	{Department of Computer Science} % Department
	{The University of Pisa} % Institution

	%------------------------------------------------

\end{supertabular}

\section{Social Skills}

With fifteen years of experience collaborating with high-performing teams, I have honed
exceptional teamwork and communication skills. A significant part of my role involves regularly
providing and receiving constructive feedback, fostering a culture of continuous improvement
by addressing challenges and acknowledging achievements.

%----------------------------------------------------------------------------------------
%	Interest and Activities
%----------------------------------------------------------------------------------------

\section{Interest and Activities}

\large Studying, Reading, Programming, History and Philosophy, Open Source, Linux, Martial Arts.

\medskip % Extra whitespace before the next section

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

\section{Languages}

\begin{tabular}{rl}
	\textsc{English:} & Professional Speaker\\

	\textsc{Italian:} & Native Speaker\\

\end{tabular}

\medskip % Extra whitespace before the next section

\switchcolumn
\newpage

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\section{Computer Skills}

% Example \tableentry{} command to add another line:

%\tableentry{Heading}{Content}{spaceafter}

% All 3 parameters must be supplied but any can be empty if you don't need them
% A "spaceafter" value in the third parameter will add some vertical space -- this is to be used between headings

%------------------------------------------------

\begin{supertabular}{rl} % Start a table with two columns, the table will ensure everything is aligned

	\tableentry{}{Golang, C, C++, Java}{}
 	\tableentry{}{Python, Javascript, Ruby, Swift }{}
	\tableentry{}{Network and System programming}{}
	\tableentry{}{Event driven programming}{}
 	\tableentry{}{Language Interoperability}{}
	\tableentry{}{Test driven development}{}
	\tableentry{}{Debugging, GDB}{}
	\tableentry{}{S.O.L.I.D, OOP, Design Patterns}{}
 	\tableentry{}{IOC/AOP}{}
  	\tableentry{}{Java Spring Boot}{}
	\tableentry{}{SQL, HQL, Sqlite, Oracle, PostgreSQL}{}
	\tableentry{}{Redis}{}
 	\tableentry{}{Kubernetes, K3s, K3d, Kind}{}
	\tableentry{}{Docker, Docker Compose, Podman}{}
 	\tableentry{}{Helm, Vagrant, Ansible}{}
	\tableentry{}{Ceph, Longhorn, Rancher}{}
	\tableentry{}{AWS S3, Minio, COSI}{}
	\tableentry{}{RabbitMQ, AMQP, MTTQ, gRPC}{}
	\tableentry{}{AsynchAPI, Swagger}{}
	\tableentry{}{Medik8s}{}
	\tableentry{}{Prometheus}{}
        \tableentry{}{Traefik, HaProxy, Nginx, Envoy}{}
        \tableentry{}{Coturn}{}
	\tableentry{}{Ginkgo, Gin}{}
	\tableentry{}{GoogleTest}{}
	\tableentry{}{V8 Javascript and WebAssembly Engine}{}
 	\tableentry{}{Qt, Boost}{}
 	\tableentry{}{Git, GitHub, GitLab, CI-CD}{}
	\tableentry{}{Shell, Scripting}{spaceafter}

\end{supertabular}

\begin{supertabular}{rl} % Start a table with two columns, the table will ensure everything is aligned

	\tableentry{Actively Studying}{Large Language Models}{spaceafter}

\end{supertabular}

%----------------------------------------------------------------------------------------

\end{paracol}

%----------------------------------------------------------------------------------------

\end{document}